### 2016-08-25 introduction.tex
minor fix

Given this set of specific needs, in this work we present the design, key step-by-step instructions and mechanisms to setup, configurate and maintain of an inexpensive testbed using potentially several \ac{Raspi} devices for networking (wireless or wired) and storage applications including \ac{RLNC} functionalities into the testbed through Kodo. Nevertheless, the architecture itself is not bounded to the networking area and can be used for other applications that require replicable results with the \ac{Raspi}. Our work for the testbed procedure is organized as follows: Section~\ref{sec:overview} introduces the testbed system. In Section~\ref{sec:image_setup}, we provide details about the testbed setup, scripts, configuration files and connectivity. In Section~\ref{sec:overlay_fs}, we elaborate on the need and setup for an overlay filesystem for our testbed in order to have both persistent and non-persistent data on it as an optional step. Section~\ref{sec:tools} describes a set of automation and monitoring tools that can be included in the testbed to simplify the execution of routinary and repetitive tasks. Section~\ref{sec:cross_compilation} elaborates on the compilation of the Kodo library for the \ac{Raspi}. Conclusions and future work are reviewed in Section~\ref{sec:conclusions}. Finally, a set of alternative commands, in case the ones presented in this work might not be executed, are discussed in the Appendices.

>>>>

Given this set of specific needs, in this work we present the design, key step-by-step instructions and mechanisms to setup, configure and maintain an inexpensive testbed using potentially several \ac{Raspi} devices for networking (wireless or wired) and storage applications including \ac{RLNC} functionalities into the testbed through Kodo. Nevertheless, the architecture itself is not bounded to the networking area and can be used for other applications that require replicable results with the \ac{Raspi}. Our work for the testbed procedure is organized as follows: Section~\ref{sec:overview} introduces the testbed system. In Section~\ref{sec:image_setup}, we provide details about the testbed setup, scripts, configuration files and connectivity. In Section~\ref{sec:overlay_fs}, we elaborate on the need and setup for an overlay filesystem for our testbed in order to have both persistent and non-persistent data on it as an optional step. Section~\ref{sec:tools} describes a set of automation and monitoring tools that can be included in the testbed to simplify the execution of routinary and repetitive tasks. Section~\ref{sec:cross_compilation} elaborates on the compilation of the Kodo library for the \ac{Raspi}. Conclusions and future work are reviewed in Section~\ref{sec:conclusions}. Finally, a set of alternative commands, in case the ones presented in this work might not be executed, are discussed in the Appendices.
